MINOS Handover Plots

### 2024-04-08 minos/validation/handovers.Rmd
Added handovers plots for age structure and population counts

out.path <- here::here('output', 'default_config/')
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
#base.dat <- read_singular_local_out(out.path, 'goodHeatingDummy', drop.dead = TRUE)
```

@@

>>>>

out.path <- here::here('output', 'glasgow_scaled/')
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE, drop.zero.weight = TRUE)
```

@@

# Age Structure

```{r}
# assign to age_bucket in raw data
cut_bins <- c(-1, 15, 19, 24, 29, 44, 59, 74, 200)
cut_labels <- c("0to15", "16to19", "20to24", "25to29", "30to44", "45to59", "60to74", "75plus")

raw.dat$age_bucket <- cut(raw.dat$age, 
                          breaks = cut_bins, 
                          labels = cut_labels)

handover_ordinal(raw.dat, base.dat, var = 'age_bucket', save = shall.we.save)
```

# Population Counts

```{r}
raw.alive <- raw.dat %>%
  group_by(time) %>%
  summarise(n = n())

base.alive <- base.dat %>%
  group_by(time) %>%
  summarise(n = n())

#handover_boxplots(raw.alive, base.alive, 'n')
handover_lineplots(raw.alive, base.alive, "n")

rm(raw.alive, base.alive)
```

# Universal Credit

```{r}
handover_ordinal(raw.dat, base.dat, var = 'universal_credit', save = shall.we.save)
```
